Synthesizing Theories of Human Language with Bayesian Program Induction

### 2018-10-24 manuscript.tex
language comparison figure

\begin{figure}
  \includegraphics[width = \textwidth]{languageComparison.png}
  \caption{Program-synthesis-based phonological rule learner applied to 37 problems from a standard phonology textbook~\cite{9780511808869}. \% data covered by rules: fraction of the phonology problem that is explained by the learned program (so 100\% does not mean a \emph{perfect} solution, but a \emph{consistent} solution). Problems marked with an asterisk are very easy problems; the other problems are more challenging. Not shown: last dozen problems in the textbook, which are very hard.}\label{languageComparison}
\end{figure}

>>>>

\begin{figure}
\centering\vspace{-3cm}  \includegraphics[width = 0.7\textwidth]{figures/languageComparison.eps}
  \caption{Program-synthesis-based phonological rule learner applied to 38 problems from a standard phonology textbook~\cite{9780511808869}. \% data covered by rules: fraction of the phonology problem that is explained by the learned program (so 100\% does not mean a \emph{perfect} solution, but a \emph{consistent} solution). Problems marked with an asterisk are very easy problems; the other problems are more challenging. Not shown: last eleven problems in the textbook, which are very hard: those results are pending.}\label{languageComparison}
\end{figure}
